Lightweight Ruby Framework for Improving Embedded Software Efficiency

### 2016-06-10 CPSNA2016/paper.tex
update CPSNA2016

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the completed software production should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
The proposed loader novelly supports a load of bytecodes.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
    \vspace{-3mm}
\caption{Component diagram of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:cyclic_handler}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

>>>>

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the completed software production should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
The proposed loader newly supports a load of bytecodes.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=1.8cm,width=8.6cm,clip]{figure/cyclic_handler.eps}
    \vspace{-3mm}
\caption{Component diagram of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:cyclic_handler}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} function and co-routine method run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
% Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.
